Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
Descriptions of benchmarks

\todo{The safety specification is defined over the state space, not the output. Further, please distinguish the spec from the input constraints. }

@@

The safety property represented by $\phi_{safety}$ is encoded as follows:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{x_{i}^{-} \leq x_{i,k} \leq x_{i}^{+}},
\end{equation}
%
\todo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}

where $x_{i}^{-}$ and $x_{i}^{+}$ are the lower and upper bound 
of the $i$-th state $x_{i}$ at the $k$-th instant, respectively.
This means that the states will always be within the $n$-dimensional 
hyper-box, which is typically defined by the safety specification.

@@

>>>>

%\todo{The safety specification is defined over the state space, not the output. Further, please distinguish the spec from the input constraints. }

@@

The safety property represented by $\phi_{safety}$ is encoded as follows:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_{safety}\iff \forall k\geq 0, \bigwedge_{i=1}^{n}{x_{i}^{-} \leq x_{i,k} \leq x_{i}^{+}},
\end{equation}
%
%\todo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
where $x_{i}^{-}$ and $x_{i}^{+}$ are the lower and upper bound 
of the $i$-th state $x_{i}$ at the $k$-th instant, respectively.
This means that the states will always be within the $n$-dimensional 
hyper-box, which is typically defined by the safety specification.

@@

These benchmarks were discretized with different sample times using the approach described in Appendix ~\ref{sec:appendix}. All the experiments were performed considering $x_{i}^{-}=-1$ and $x_{i}^{+}=1$ and the inputs $u_{k}=0, \forall k>0$.
